# Data Analysis {#intro}

## GitHub Repositories

what to put on github
what NOT to put on github
where to put files - R drive; OneDrive; Google Drive
where to put code - local & repo
* no data, no output; should be able to regenerate these with 1 click
* folder structure: data; output, code (functions only)
+  sructure of a project
- .rmd files on root directory
- output directory
- code direcotry: R code files containing functions that you call
- all other R code should be right in the rmd file
- SOURCE dependencies (code in R folder) at top of .rmd file that needs them, along with libraries needed for that file.
* how to ignore something: GitIgore (how to add to it: folders; file types, specific files)
























You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
