# Data Analysis {#intro}

## GitHub Repositories

what to put on github
what NOT to put on github
where to put files - R drive; OneDrive; Google Drive
where to put code - local & repo
* no data, no output; should be able to regenerate these with 1 click
* folder structure: data; output, code (functions only)
+  sructure of a project
- .rmd files on root directory
- output directory
- code direcotry: R code files containing functions that you call
- all other R code should be right in the rmd file
- SOURCE dependencies (code in R folder) at top of .rmd file that needs them, along with libraries needed for that file.
* how to ignore something: GitIgore (how to add to it: folders; file types, specific files)


## Steps in every analysis

1) Read in data, get into Tidy format

2) Manipulate data as needed

3) Visualize data

use ggplot2 package

Always do this before any statistical analysis.  Look at the data to see what is going on.  After that you can do statistical analysis (e.g., ANOVA/regression, t-tests, etc.) to see if any obsered differences are large enough to be considered reliable (i.e., "statistically significant"). 

You should have plots summarizing each of your variables, as well as combinations of variables that are obviously of importance (e.g., block x accuracy)

Types of plots for variable types:
- 2 continuous variables (e.g., age, height): scatterplot (GGPLOT); line (GGPLOT)
etc...

4) Statistical analysis

5) Data modeling 

























You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
