# Data Analysis {#intro}

## GitHub Repositories

what to put on github
what NOT to put on github
where to put files - R drive; OneDrive; Google Drive
where to put code - local & repo
* no data, no output; should be able to regenerate these with 1 click
* folder structure: data; output, code (functions only)
+  sructure of a project
- .rmd files on root directory
- output directory
- code direcotry: R code files containing functions that you call
- all other R code should be right in the rmd file
- SOURCE dependencies (code in R folder) at top of .rmd file that needs them, along with libraries needed for that file.
* how to ignore something: GitIgore (how to add to it: folders; file types, specific files)


## Steps in every analysis

1) Read in data, get into Tidy format

2) Manipulate data as needed

3) Visualize data

use ggplot2 package

Always do this before any statistical analysis.  Look at the data to see what is going on.  After that you can do statistical analysis (e.g., ANOVA/regression, t-tests, etc.) to see if any obsered differences are large enough to be considered reliable (i.e., "statistically significant"). 

You should have plots summarizing each of your variables, as well as combinations of variables that are obviously of importance (e.g., block x accuracy)

Types of plots for variable types:
- 2 continuous variables (e.g., age, height): scatterplot (GGPLOT); line (GGPLOT)
etc...

4) Statistical analysis

>> data analysis
1) - scale types: ALWAYS consider first!
> metric, ordinal, etc
> need to know this for plotting and statistical analysis
2) - long form vs wide form data; transforming between these
>> important for plotting, ANOVA, 
2.5) data assumption: normally distributed?  y = data; completely unknown; normal? tests
3) general linear model
>> correlation; simple regression, multiple regression
>>> prediction- yes!  causation - no!
>>> causation - need experiment (control timing of cause(s)!! (only way w obs data = SEM/BAYES NETS)
> ttest logic
> anova logic
> ANOVA is a special case of regression with dichotomos predictors! (same mathematical model)
> what is the linear model doing?  linear equation + normally distributed noise
>>> assumption of the model - normally distributed data ==> the NOISE!! (unexplained variance part). 
> 

how do do anovas/regression w software
>> spss
>> jasp
>> R

how to interpret & report results (APA style; what to report; how to INTERPRET!)
>> ANOVA 
>> regression? 

> what if assumptions are violated? 
>> nonparametric statistical tests (robust to violations)

frequentist (classical) vs bayesian statistics
>> why? replicability!
>> problems w classical (multiple comparisons; null hypothesis not what we want, no peeking/cheating!) 
>> problems solved by bayesian
>> is NHST/classical worthless?  NO!!  its just that bayesian seems to be BETTER (more reliable by avoiding some of the problems that reduce reliability in terms of reproducability (replicability)
> statistics is about REPLICATILBITY
> replicability is about what is true!  
> we want to avoid publishig things that are not true! we want us (and others) to be able to replcate; bayesian may help us play it safer

so what do we do in stats? 2 things
1) estimation (e.g., mean, variance, difference between groups, learning rate, regreession coefficient)
2) inference (e.g., difference between groups?  effect of treatement? theory/model 1 better than theory/model 2?)
note: both classical and bayesian apply the SAME MODEL!! GENERAL LINEAR MODEL
>> they differ in terms of how they ESTIAMTE the parameters of the model(s)
>> they differ in how we INTERPET THE RESULTS (i.e., make infernces from the data!)







5) Data modeling 









misc
>> switching between long & short data types
>> page for this?  blog post demonstrations? both? 
>> important: data types -boring but essential; need to master this as it underlies proper use of functions and many errors are related to mis-use
















You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
