--- 
title: "CDL Virtual Advisor (Lab Manual)"
author: "Corey Bohil"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This document contains guidelines and how-to examples for members of the CDL.  It should be a useful resource for all lab members, but particularly for new members"
---

# Overview

The goal of this book is to serve as a resource for procedures in the lab, tutorials on software and hardware use, and some other advice that I hope will be helpful (e.g., advice on scientific manuscript writing).  My guess is that it will serve primarily to get people started in the lab, and also as a refresher on some details about data handling/analyis and use of some equipment.

This is a living document.  We should update it regularly.

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
